Use and acquisition of causal relations for decision making under uncertainty using imperfect information games

### 2018-08-16 Propuesta/Formato/Proposal_format.tex
modificando los casos segun el principio guia

The three cases that we notice are:
\begin{itemize}
\item The decision maker knows the causal model.
\item The decision maker knows only the graphical \textit{structure} of the causal model.
\item The decision maker knows nothing about the causal model. 
\end{itemize}
In the following we show how the first two cases, which are particular cases of our general problem, can be solved and we show that the proposed solution for the first two cases sheds light on how the general case could be solved.
\subsubsection{Fully knowing the causal graphical model}
If the decision maker knows the causal graphical model, then he could easily calculate the effect on the target variable that any of his actions has and then choose the action that has the highest probability of causing a \textit{desired} value of the target variable. The decision thus made is the one that maximizes the expected utility, by construction. Also, choosing this action is the \textit{best response} action, and therefore a Nash equilibrium for the game. Choosing the action that is more likely to produce the most desired outcome according to current causal knowledge is required by Joyce's Causal Decision Theory (\cite{joyce1999foundations}).
\subsubsection{Knowing only the graph structure}
If a decision maker knows the structure of the graph, but he does not know the parameters, then he encodes this ignorance, along with any useful previous knowledge, as a probability distribution over a suitable space. In the preliminary results that will be shown later a particular case is considered, where the beliefs have the form of a Dirichlet distribution for each of the Conditional Probability Tables that characterize a Bayesian Network.

In general, what must be specified is a way of encoding current causal knowledge into a probability distribution in such a way that a \textit{local} (i.e. in each round) causal model can be obtained from current beliefs in order to make a decision using current causal knowledge and those beliefs will be later updated using what is observed after choosing an action.  
\subsubsection{General case: Model unknown}
The previous two cases are per se steps of the methodology, rather simplifications in order to understand what is happening. The real deal is the case where the causal model is unknown.

>>>>

The three cases that we notice are:
\begin{itemize}
\item The decision maker knows the causal model.
\item The decision maker knows only the graphical \textit{structure} of the causal model.
\item The decision maker knows nothing about the causal model. 
\end{itemize}
In the following we show how the first two cases, which are particular cases of our general problem, can be solved and we show that the proposed solution for the first two cases sheds light on how the general case could be solved.
\subsubsection{Fully knowing the causal graphical model}
If the decision maker knows the causal graphical model, then following the guiding principle, he could easily calculate the effect on the target variable that any of his actions has and then choose the action that has the highest probability of causing a \textit{desired} value of the target variable. The decision thus made is the one that maximizes the expected utility, by construction. Also, choosing this action is the \textit{best response} action, and therefore a Nash equilibrium for the game. Choosing the action that is more likely to produce the most desired outcome according to current causal knowledge is required by Joyce's Causal Decision Theory (\cite{joyce1999foundations}).
\subsubsection{Knowing only the graph structure}
If a decision maker knows the structure of the graph, but he does not know the parameters, then he encodes this ignorance, along with any useful previous knowledge, as a probability distribution over a suitable space. In the preliminary results that will be shown later a particular case is considered, where the beliefs have the form of a Dirichlet distribution for each of the Conditional Probability Tables that characterize a Bayesian Network.

In general, what must be specified is a way of encoding current causal knowledge into a probability distribution in such a way that a \textit{local} (i.e. in each round) causal model can be obtained from current beliefs in order to make a decision using current causal knowledge and those beliefs will be later updated using what is observed after choosing an action.  The action will be chosen, given a set of beliefs, as in the previous case and by following the guiding principle. This means that using current beliefs, the agent forms a causal model which is used as if it were the true causal model.
\subsubsection{General case: Model unknown}
The previous two cases are per se steps of the methodology, rather simplifications in order to understand what is happening. The real deal is the case where the causal model is unknown.
